---
title: "Course 9 week 4 - Pricing Diamonds After Property"
author: "Mikael Helin"
date: '2019-04-23'
output:
  slidy_presentation: default
  beamer_presentation: default
  ioslides_presentation: default
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

---

Average diamond price (in USD) for different cuts.

```{r plot1, message=FALSE}
library(plotly)
data("diamonds",package="ggplot2")
plot_ly(diamonds, x = ~cut, name="")
```

---

Diamonds priced (in USD) after weight in carats.

```{r plot2, message=FALSE}
plot_ly(diamonds, x = ~carat)
```

Weight alone does not have dominant role in pricing diamonds. It appears that other properties, such as cut, plays an important role in pricing diamonds.

---

Diamonds priced (in USD) after clarity.

```{r plot3, message=FALSE}
plot_ly(diamonds, x = ~clarity)
```

Measurement of how clear the diamond is: I1 (worst), SI2, SI1, VS2, VS1, VVS2, VVS1, IF (best).

---

The most easy way to price a diamond is to use the interactive linear predictor at

https://mikael-helin.shinyapps.io/Pricing_Diamonds/

By use of this predictor, you may estimate the price for arbitrary diamonds.


